%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{muchicv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Sorin Muchi}
%\address{Vancouver, BC}
\contacts{github.com/sorinmuchi \linebreak sorin.muchi@gmail.com \linebreak (514) 431-5451}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Fortinet}{Software Engineer}{Sept 2017 - now}
			%FortiOS Web UI development.
			\begin{itemize}
				\item Introduced new licenses, which increased revenue, by implementing the UI for the underlying features.
				\item Improved customer satisfaction by fixing high-impact customer support bugs across the entire web stack.
				\item Provided visibility into user interactions with our product by prototyping a telemetry solution.
				\item Ranked 2nd out of 10 in an internal company-wide CTF-style network security competition.
				\item Stack: C, Python, JavaScript, Apache, Django, AngularJS, Stylus, CSS, REST API
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Microsoft, Microsoft Garage}{Software Engineer Intern}{May - Aug 2017}
			%Microsoft Garage, internship in a startup-like environment. Full systems development life cycle.
			\begin{itemize}
				\item Led a team of 6 interns to build a user-centric design-focused iOS transit application and scalable backend.
				\item Exceeded project's Machine Learning requirements by building a ML pipeline able to predict bus crowdedness per stop per time of day at 80--90\% accuracy levels.
				\item Stack: Azure, ASP.NET, C\#, Xamarin, iOS, Deep Neural Networks, Decision Trees, SVMs, Python
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Genetec}{Software Engineer Intern}{Jan - Aug 2016}
			%Sipelia Team, A/V communication for a physical security solution.
			\begin{itemize}
				\item Expanded product integrations by 10\% by fixing critical SIP stack bugs and certifying the compatibility of several 3rd party devices.
				\item Improved customer satisfaction by implementing GUI features requested by key customers.
				\item Stack: F\#, Erlang, C\#, SIP, Audio/Video Codecs, UDP
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Social Orra}{Software Engineer Intern}{May - Aug 2015}
			%Social Media management startup
			\begin{itemize}
				\item Bootstrapped the company's MVP by prototyping a full stack web application for a social media management startup.
				\item Stack: Java, Scala, JavaScript, Akka, Play, AngularJS
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Ericsson}{Software Engineer Intern}{May - Aug 2014}
			%Content Delivery Network Team.
			\begin{itemize}
				\item Increased logging efficiency in production by 10x by migrating the logging system from LOG4J to SLF4J.
				\item Stack: Java, Bash, Unix
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{McGIll University}{B.A. Computer Science}{Sept 2013 - Apr 2017}
			\begin{itemize}
				\item \textbf{Image Classification Machine Learning Competition.} (2017) Placed 3/50 in mixed Ugrad/Grad class contest.
				\item \textbf{Sponsorship Lead, Hack McGill.} (2015-17) Led a sponsorship team of 3 to raise \$100k/yr. 10\% increase YOY.
				\item \textbf{CS Tutor, CS Undergrad Society.} (2015) Held weekly office hours, tutoring Computer Science students.
				\item \textbf{Arts and Science 1971 International Bursary.} (2013) Merit based entrance scholarship awarded to select students from former Warsaw Pact countries.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{Self-Driving Car Nanodegree, Udacity} (2018) Deep Learning and Computer Vision projects. TensorFlow, Keras
				\item \textbf{Image Classification} (2017). ImageNet subset image classification. 3rd pl. 91\% 1-class acc. ML. TensorFlow.
				\item \textbf{Settlers of Catan} (2017).  3D P2P multiplayer implementation of the classic board game, using Unity.
				\item \textbf{NoteEx} (2016). Gameified note exchange platform for students. Ruby, Ruby on Rails, JavaScript, jQuery.
				\item \textbf{Russian Transliteration} (2015). Chrome plugin to introduce tooltips with phonetics for Cyrillic text. Hackathon.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Languages}: JavaScript,  ES6+, Python, Java, C, F\#, C\#, OCaml, SQL 
				\item \textbf{Frameworks}: Django, AngularJS, Express, Ruby on Rails
				\item \textbf{Machine Learning}: Keras, TensorFlow, pandas, NumPy, scikit-learn, OpenCV
				\item \textbf{Other}: Linux, git, TCP/IP, jQuery, gulp, grunt
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
